---
title: "klink"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{klink}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## What it's for
klink is an internal R package intended to provide helpful functions focused on easily forming connections to data sources.

## Setup
In order to use these tools users must first:

1. Have an RStudio Connect account (you likely have one already if you're using RStudio Workbench, if not you can request access through Digital Concierge, instructions can be found here: <https://rstudioconnect.analytics.kellogg.com/RStudio_Knowledge_Library/>)
2. Create a local RStudio Connect API key <https://docs.rstudio.com/connect/user/api-keys>
3. Create an .Renviron file in your Home folder assigning your API key value to the name CONNECT_API_KEY <https://rstats.wtf/r-startup.html>

## How to Install
Currently, the easiest way to install the klink package is to install from the public GitHub repo:
```{r install, eval=FALSE, include=TRUE}
devtools::install_github("mikechappelow/klink")

library(klink)
```

In the future we will host these types of packages in our internal RStudio Package Manager environment.

## Current Functions

### klink functions
The klink functions are a general group of functions used to establish links to data sources commonly used within Kellogg.

#### klink_sql
The klink_sql function enables users to link to predefined, internal SQL databases using only a couple of arguments and removes the necessity of locally defining service account credentials in your code, .Renviron files, and/or manually assignment in Connect publications.

```{r klink_sql, eval=TRUE, include=TRUE}
library(klink)
library(DBI)
library(odbc)

conn <- klink_sql("DEV", "KG_ANALYTICS_APPS")

dbGetQuery(conn,
          "SELECT TOP 5
          fixer_number, service_provider
          FROM dbo.GBS_Performance_Metrics;")
```

#### klink_s3R
The klink_s3R function enables users to define all of the required settings and variables required to link to our foreign s3 bucket simply by calling the function.

```{r klink_s3R, eval=TRUE, include=TRUE}
library(klink)
library(aws.s3)

# Retrieve required system settings (in background) and appropriate s3 bucket name
klink_s3R()

# Use aws.s3 functions to retrieve information from s3 bucket
aws.s3::object_exists("/data/R_training/package_list.rds", bucket = s3BucketName)
aws.s3::object_size("/data/R_training/package_list.rds", bucket = s3BucketName)
```

### zoltar
The klink functions are essentially wrappers that utilize zoltar to make the user experience as lightweight as possible by making implicit assumptions about the connection that should be formed.

If you would like to override these assumptions by specifying your own connection settings zoltar is the solution.

When a wish/alias of a known value is passed to this function our internal zoltar API returns the requested value. 

If there are required connections that are not yet supported by zoltar please reach out to the Kellogg Data Science team to have them added.

```{r zoltar, eval=FALSE, include=TRUE}
library(klink)

zoltar("s3BucketName")
```
